pirouette: Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-03-14 article.tex
Give listings labels

\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
pir_params <- create_pir_params(
  alignment_params = alignment_params,
  experiments = experiments,
  error_measure_params = create_error_measure_params(),
  twinning_params = NA
)
\end{lstlisting}

@@

\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
errors <- pir_run(
  phylogeny = phylogeny,
  pir_params = pir_params
)
\end{lstlisting}

@@

@@

In the second step we set up our experiments. 
Within this ERQ, each of our experiments contain a different
inference model $I$, but has condition $C$ that will only let $I$
be run in inference if that inference model $I$ is the 
best candidate inference model, that is, 
it is the inference model with the highest evidence.
Setting up experiments like this is thought to be so common,
that \verb;pirouette; has a simple function to do:
\verb;create_all_experiments; will create 40 experiments,
containing inference models of all combinations of 4 site 
models, 2 clock models and 5 tree priors.

@@

For all other steps we use the default setups. 
We can create the complete
\verb;pirouette; parameter set like this:

\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
pir_params <- create_pir_params(
  alignment_params = alignment_params,
  experiments = experiments
)
\end{lstlisting}

\begin{lstlisting}[language=R, floatplacement=ht, frame=single]
errors <- pir_run(
  phylogeny = phylogeny,
  pir_params = pir_params
)
\end{lstlisting}

The resulting figure is shown in figure~\ref{fig:example_2}.

>>>>

\begin{lstlisting}[
  language=R, floatplacement=ht, frame=single,
  label = {lst:create_pir_params},
  caption = Calling \texttt{create\_pir\_params}
]
pir_params <- create_pir_params(
  alignment_params = alignment_params,
  experiments = experiments,
  error_measure_params = create_error_measure_params(),
  twinning_params = NA
)
\end{lstlisting}

@@

\begin{lstlisting}[
  language=R, floatplacement=ht, frame=single,
  label = {lst:pir_run},
  caption = Calling \texttt{pir\_run}
]
errors <- pir_run(
  phylogeny = phylogeny,
  pir_params = pir_params
)
\end{lstlisting}

@@

\begin{lstlisting}[
  language=R, floatplacement=ht, frame=single,
  label = {lst:pir_plot},
  caption = Calling \texttt{pir\_plot}
]
pir_plot(errors)
\end{lstlisting}

@@

In the second step we set up our experiments. 
Within this ERQ, each of our experiments contain a different
inference model $I$, but has condition $C$ that will only let $I$
be run in inference if that inference model $I$ is the 
best candidate inference model, that is, 
it is the inference model with the highest evidence.
Setting up experiments like this is thought to be so common,
that \verb;pirouette; has a simple function to do:
\verb;create_all_experiments; will create 40 experiments,
containing the inference models of all combinations of 4 site 
models, 2 clock models and 5 tree priors.

@@

For all other steps we use the default setups. 
We can create the complete
\verb;pirouette; parameter set like this (which is the
same as listing~\ref{lst:create_pir_params}, but using the defaults):

\begin{lstlisting}[
  language=R, floatplacement=ht, frame=single,
  label = {lts:create_pir_params_defaults},
  caption = Create a \texttt{pir\_params} with many defaults
]
pir_params <- create_pir_params(
  alignment_params = alignment_params,
  experiments = experiments
)
\end{lstlisting}

We can run the \verb;pirouette; method with listing~\ref{lst:pir_run}
and plot the results with listing~\ref{lst:pir_plot}.
The resulting figure is shown in figure~\ref{fig:example_2}.
